Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-08-17 article.tex
Bumped DCC number
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1357 ccdd05d5-56c1-461a-bf98-85f6876523b4
Clarified that we are talking about median mismatch
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1360 ccdd05d5-56c1-461a-bf98-85f6876523b4

We studied how the \SVD\ tolerance affected \SNR\ loss by holding
$N^\shortdownarrow = N^\shortuparrow = 192$ fixed as we varied the \SVD\
tolerance from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.  The
minimum, maximum, and median mismatch are shown as functions of \SVD\ tolerance
in Figure~\ref{fig:bw}a.  As the \SVD\ tolerance increases toward 1, the \SVD\
becomes an exact matrix factorization, but the computational cost increases as
the number of basis filters increases.  The conditions presented here are more
complicated than in the original work~\citep{Cannon:2010p10398} due to the
inclusion of the time-sliced templates and interpolation, though we still see
that the average mismatch is approximately proportional to the \SVD\ tolerance
down to $\left(1-10^{-4}\right)$.  However, as the \SVD\ tolerance becomes even
higher, the mismatch seems to saturate around $2 \times 10^{-4}$.  This could be
the effect of the interpolation, or an unintended technical imperfection that we
did not model or expect.  However, this is still an order of magnitude below our
target mismatch of 0.003.  We find that an \SVD\ tolerance of
$\left(1-10^{-4}\right)$ is adequate to achieve our target \SNR\ loss.

@@

Having selected an SVD tolerance of $\left(1-10^{-4}\right)$ and
$N^\shortuparrow=16$, we found that we could reduce $N^\shortdownarrow$ to 48
without exceeding a maximum mismatch of~0.003.

@@

This paper has \LIGO\ Document Number {LIGO-P0900004-v27}.

>>>>

We studied how the \SVD\ tolerance affected \SNR\ loss by holding
$N^\shortdownarrow = N^\shortuparrow = 192$ fixed as we varied the \SVD\
tolerance from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.  The
minimum, maximum, and median mismatch are shown as functions of \SVD\ tolerance
in Figure~\ref{fig:bw}a.  As the \SVD\ tolerance increases toward 1, the \SVD\
becomes an exact matrix factorization, but the computational cost increases as
the number of basis filters increases.  The conditions presented here are more
complicated than in the original work~\citep{Cannon:2010p10398} due to the
inclusion of the time-sliced templates and interpolation, though we still see
that the average mismatch is approximately proportional to the \SVD\ tolerance
down to $\left(1-10^{-4}\right)$.  However, as the \SVD\ tolerance becomes even
higher, the median mismatch seems to saturate around $2 \times 10^{-4}$.  This
could be the effect of the interpolation, or an unintended technical
imperfection that we did not model or expect.  However, this is still an order
of magnitude below our target mismatch of 0.003.  We find that an \SVD\
tolerance of $\left(1-10^{-4}\right)$ is adequate to achieve our target \SNR\
loss.

@@

Having selected an SVD tolerance of $\left(1-10^{-4}\right)$ and
$N^\shortuparrow=16$, we found that we could reduce $N^\shortdownarrow$ to 48
without exceeding a median mismatch of~0.003.

@@

This paper has \LIGO\ Document Number {LIGO-P0900004-v28}.
